---
title: "sketchy"
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}

# knitr global options
knitr::opts_chunk$set(
  collapse = TRUE,
  out.width = "100%",
  tidy = TRUE
)
library(sketchy)

```

[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/sketchy)](https://cran.r-project.org/package=sketchy)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/sketchy)](http://www.r-pkg.org/pkg/sketchy)
[![Total downloads](https://cranlogs.r-pkg.org/badges/grand-total/sketchy?color=blue)](https://r-pkg.org/pkg/sketchy)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)


The package is intended to facilitate the use of research compendiums for data analysis in the R environment. Standard research compendiums provide a easily recognizable means for organizing digital materials, allowing  other researchers to inspect, reproduce, and build upon that research. 

<!-- Unlike other packages for setting up research compendiums, `sketchy` has very simple functionality. Hence, users can focus on the research project itself rather than on learning how to use a new R package. -->

Unlike other R packages for creating research compendiums (e.g. [vertical](https://github.com/CrumpLab/vertical), [rrtools](https://github.com/benmarwick/rrtools)), `sketchy` isn't  wedded to a particular folder structure. Currently the package provides `r length(compendiums)` alternative structures (see object `compendiums`) and allows users to modify or input their own structures.   

To install the latest developmental version from [github](https://github.com/) you will need the R package [remotes](https://cran.r-project.org/package=remotes):

```{r, eval = FALSE}

# From github
remotes::install_github("maRce10/sketchy")

#load package
library(sketchy)

```

```{r, echo = FALSE}

load("./data/compendiums.rda")
```


## Default compendium skeletons

Compendiums can be set up with the function `make_compendium()`. The function creates the folder/subfolder structure and prints a diagram of the skeleton in the console:

### Basic compendium

```{r, eval = TRUE}

path = tempdir()

make_compendium(name = "proyect_x", path = path, format = "basic")

```


&nbsp; 

(*in these examples the compendiums are created in a temporary directory, change 'path' to create it in a different directory*)


### Alternative structures

We can use folder structures from other sources. For instance, in this example we use the structured suggested by Wilson *et al.* (2017):

```{r, eval = TRUE}

make_compendium(name = "proyect_y", path = path, format = "sketchy",
                comments = FALSE)

```
&nbsp; 

We can also add comments to the folders to explain what kind of files they are supposed to contain: 

```{r, eval = TRUE}

make_compendium(name = "proyect_z", path = path, format = "large_compendium", 
                    comments = TRUE)

```

&nbsp; 

When creating a compendium that includes a "manuscript" folder the package adds a "manuscript_template.Rmd" file for facilitating paper writing within the compendium itself.


We can check all compendium structure available as follows:

```{r, eval = TRUE}

for(i in 1:length(compendiums)){
  print("---------------", quote = FALSE)
  print(names(compendiums)[i], quote = FALSE)
  print_skeleton(folders = compendiums[[i]]$skeleton)
}
  
```
---

Please cite [sketchy](https://marce10.github.io/sketchy/) as follows:

Araya-Salas, M., Willink, B., Arriaga, A. (2020), *sketchy: research compendiums for data analysis in R*. R package version 1.0.0. 


# References

1. Alston, J., & Rick, J. (2020). *A Beginner’s Guide to Conducting Reproducible Research*. 

1. Marwick, B., Boettiger, C., & Mullen, L. (2018). *Packaging Data Analytical Work Reproducibly Using R (and Friends)*. American Statistician, 72(1), 80–88.

1. Wilson G, Bryan J, Cranston K, Kitzes J, Nederbragt L. & Teal, T. K.. 2017. *Good enough practices in scientific computing*. PLOS Computational Biology 13(6): e1005510.
